Exploring the evolution of stellar rotation using Galactic kinematics

### 2020-03-18 paper/acknowledgements.tex
Elisabeth's comments and some of Gus's
adding jen's small comments and a core-envelope coupling section
changing bib and adding acknowledgement

This work was partly developed at the 2019 KITP conference 'Better stars,
better planets'.
Parts of this project are based on ideas explored at the Gaia sprints at the
Flatiron Institute in New York City, 2016 and MPIA, Heidelberg, 2017.

>>>>

We would like to thank Suzanne Aigrain for providing thoughtful insight that
improved this paper.

This work was partly developed at the 2019 KITP conference `Better stars,
better planets'.
This research was supported in part by the National Science Foundation under
Grant No. NSF PHY-1748958.

Parts of this project are based on ideas explored at the Gaia sprints at the
Flatiron Institute in New York City, 2016 and MPIA, Heidelberg, 2017.
